---
title: "Multiple Linear Regression. Advertising case"
author: "I. Maslova"
date: today
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

Suppose are hired a data science consultants hired by a client to provide advice on how to improve sales of a particular product. It is not possible for our client to directly increase sales of the product. On the other hand, they can control the advertising expenditure in each of the three media. Therefore, if we determine that there is an association between advertising and sales, then we can instruct our client to adjust advertising budgets, thereby indirectly increasing sales. In other words, our goal is to develop an accurate model that can be used to predict sales on the basis of the three media budgets.

•	Which media contribute to sales?
•	Which media generate the biggest boost in sales? or
•	How much increase in sales is associated with a given increase in TV advertising?

What information would be useful in order to provide such a recommendation? Here are a few important questions that we might seek to address:

Data: 

The Advertising data set consists of the sales ( in thousands of units) of that product in 200 different markets, along with advertising budgets (in thousands of dollars) for the product in each of those markets for three different media: TV, radio, and newspaper. 

 Business questions: 

Is there a relationship between advertising budget and sales?

Our first goal should be to determine whether the data provide evidence of an association between advertising expenditure and sales. If the evidence is weak, then one might argue that no money should
be spent on advertising!

How strong is the relationship between advertising budget and sales?

Assuming that there is a relationship between advertising and sales, we would like to know the strength of this relationship. In other words, given a certain advertising budget, can we predict sales with a high level of accuracy? This would be a strong relationship. Or is a prediction of sales based on advertising expenditure only slightly better than a random guess? This would be a weak relationship.

Which media contribute to sales?
Do all three media—TV, radio, and newspaper—contribute to sales, or do just one or two of the media contribute? To answer this question, we must find a way to separate out the individual effects of each medium when we have spent money on all three media.

How accurately can we estimate the effect of each medium on sales?
For every dollar spent on advertising in a particular medium, by what amount will sales increase? How accurately can we predict this amount of increase?

How accurately can we predict future sales?
For any given level of television, radio, or newspaper advertising, what is our prediction for sales, and what is the accuracy of this prediction?

Is the relationship linear?
If there is approximately a straight-line relationship between advertising expenditure in the various media and sales, then linear regression is an appropriate tool. If not, then it may still be possible to transform the predictor or the response so that linear regression can be used.

Is there synergy among the advertising media?
Perhaps spending $50,000 on television advertising and $50,000 on radio advertising results in more sales than allocating $100,000 to either television or radio individually. In marketing, this is known as a synergy effect, while in statistics it is called an interaction effect.


Technical note: linear regression can be used to answer each of these questions.

@.	Set working directory.

@.	Import data in R.

```{r}
data<-read.csv("Advertising.csv")
```

@.	Create a scatter plot: sales versus TV advertising expenditures. Comment on the pattern.

```{r}
attach(data)
plot(TV, sales)
```

@. Fit the regression model to predict sales based on TV advertising.

```{r}
data.lm<-lm(sales~TV, data = data)
data.lm
```

@. Is the association between the sales and TV advertising significant?

```{r}
summary(data.lm)
```

@. Are the model assumptions met?

```{r}
plot(data.lm)

plot(TV, sales)
abline(data.lm, col="red")

acf(data.lm$residuals)
```

@. Perform a transformation to fix the assumptions. Re-run all steps of the model. 
Did it help?
```{r}
plot(log(TV), log(sales))
#plot(TV^2, sales) didn't work

data.lm.a <- lm(log(sales)~log(TV), data=data)
data.lm.a

plot(log(TV), log(sales))
abline(data.lm.a, col="red")

plot(data.lm.a, which = 1:3)
#why only look 3 plots here?
#log log does not fix the issue because the shape of residual check is not ideal
```


@. Build a SLR model using the advertising from the radio as a predictor. Plot a scatterplot, fit the model, check whether the association is significant, check the assumptions.

```{r}

plot(radio, sales)

data.lm2 <- lm(sales~radio, data = data)
data.lm2

summary(data.lm2)

plot(data.lm2, which = 1:3)

abline(data.lm2, col="red")

acf(data.lm2$residuals)
# checking the independence of the residuals
    
    ```


@. Build a SLR model using newspaper advertising as an independent variable. Plot a scatterplot, fit the model, check whether the association is significant, check the assumptions.
```{r}
plot(newspaper, sales)
cor(newspaper, sales)

data.lm3 <- lm(sales~newspaper, data=data)
data.lm3
summary(data.lm3)
plot(data.lm3, which = 1:3)
#the first three plots

plot(newspaper, sales)
abline(data.lm3, col="red")

acf(data.lm3$residuals)
```
@. Report coefficient of determination for each model. 

```{r}
R2.TV <- summary(data.lm)$adj.r.squared
R2.radio <- summary(data.lm2)$adj.r.squared
R2.newspaper <- summary(data.lm3)$adj.r.squared
#coefficient of determination= r-square?
```
The adjusted $R^2$ for the sales vs TV model is `r round(100*R2.TV, 1)` percent.

The adjusted $R^2$ for the sales vs radio model is `r round(100*R2.radio, 1)` percent.

The adjusted $R^2$ for the sales vs newspaper model is `r round(100*R2.newspaper, 1)` percent.


@. Compute the residual standard deviation CV (Coefficient of variation). 

CV = RMSE/mean of Y

Rule of thumb: predictions are accurate if CV is no more than 10%.
```{r}
CV1=100*summary(data.lm)$sigma/mean(sales)
CV2=100*summary(data.lm2)$sigma/mean(sales)
CV3=100*summary(data.lm3)$sigma/mean(sales)
CV1
CV2
CV3
```
@. Which predictor is the best in modeling and predicting the sales. Explain how you decided.

Note: CV evaluates the relative closeness 
of the predictions to the actual values while $R^2$ 
evaluates how much of the variability in the actual 
values is explained by the model.

Simple linear regression is a useful approach for predicting a response on the basis of a single predictor variable. However, in practice we often have more than one predictor. In the Advertising data we have examined the relationship between sales and TV, radio and newspaper advertising separately. We may want to know whether either of these two media is associated with sales. How can we extend our analysis of the advertising data in order to accommodate these two additional predictors?

A: Among the three predictors, TV is the best in predicting the sales because it has the highest r square and the lowest CV

@. Is the approach of fitting a separate simple linear regression model for each predictor satisfactory? Explain.

No, none of the models are particularly good because the r square are low, the CV are all above 10% and the independence of residuals(acf plot) are not ideal.

@.	Fit a multiple regression model to predict sales from TV, radio, and newspaper advertising budgets simultaneously and compare model parameter estimates with corresponding simple regression estimates. 

```{r}
data.mlm <- lm(sales~TV+radio+newspaper, data=data)
data.mlm
pairs(data.mlm)
#cannot coerce class ‘"lm"’ to a data.frame
```
@.	Does it make sense for the multiple regression to suggest no relationship between sales and newspaper while the simple linear regression implies the opposite?

```{r}
summary(data.mlm)
cor(data[,-1])
#variance inflation factor
#variance not to be inflated, take it out will be the same, close to one

```
@. Is there a multicollinearity in the model?

@. When we perform multiple linear regression, we usually are interested in answering a few important questions.

•	Is at least one of the predictors $X_1,X_2, . . . , X_p$ useful in predicting the response? 

```{r}
install.packages("car")
library(car)
vif(data.mlm)
?vif
```
•	Do all the predictors help to explain Y , or is only a subset of the predictors useful?

•	How well does the model fit the data?

•	Given a set of predictor values, what response value should we predict, and how accurate is our prediction?


@.	Is at least one of the predictors $X_1,X_2, . . . , X_p$ useful in predicting the response? If yes, which one(s)?

Yes, the F-test is significant, i.e.that at least one predictor effect is real. The follow-up analysis show that TV and radio advertising are significant and should be kept in the model.

@. Are the rest of the assumptions met?

@. Build a model to predict sales from TV and radio advertising. 

```{r}
data.mlm2 <- lm(sales~TV+radio, data=data)
data.mlm2

summary(data.mlm2)
```
@. Given that $100,000 is spent on TV advertising and $20,000 is spent on radio advertising in each city make prediction of sales and construct a 95% prediction interval. Interpret the prediction interval.

Prediction confidence interval gives the uncertainty of the prediction for a particular city.

Confidence interval estimates the spread around average sales across large cities.

```{r}
new.data <- data.frame(TV=100, radio = 20)
p.ci <- predict(data.mlm2, new.data, se.fit = T, interval="prediction")

c.ci <- predict(data.mlm2, new.data, se.fit = T, interval="confidence")
p.ci$fit
c.ci$fit
```

